Knowledge and the Web: Homework 3

### 2015-11-12 homework_3/hw3.tex
data sources vraag 3

\end{document}

>>>>

\paragraph{\textbf{European Union Open Data Portal} (\url{https://open-data.europa.eu/})} contains datasets about homicides and other criminal activities e.g. homicide offences. This data necessary to determine if location influences the chance of being murdered.

\paragraph{\textbf{Freebase} (\url{https://www.freebase.com/})} This is a knowledge base specialized among others in well-known people. Because most politicians are well-known this is a interesting knowledge base. Furthermore in Freebase is the property \textit{cause\_of\_death} which we can use to find murders or homicides among the politicians.

\paragraph{\textbf{DBpedia} (\url{http://wiki.dbpedia.org/})}
For this question we need also some background information. As already pointed out, DBpedia is a good source for this.
\end{document}
